\blue{Numerical Investigation of Multi-Fluid Flows through Dual Saturated-Unsaturated Porous Media - change the title to something close to the main topic of the manuscript ... something with viscous flow instability or viscous fingering)}

### 2017-03-03 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updated

\noindent The purpose of these two cases was to verify that our model is working for cases that experimentally are proven. This will allow to proceed further and expand this technique into more complex formations. A more detailed description of the element type and the formation that will be used in the next set of test cases follows.

\begin{figure}[h]
\makebox[\textwidth]{%
\subfigure[MR1]{%
\includegraphics[width=0.49\textwidth]{./Pics1/mr1_fixed/mr1_fixed_100_2.pdf}%
}%
\hfill    
\subfigure[MR10]{%
\includegraphics[width=0.49\textwidth]{./Pics1/mr10_fixed/mr10_fixed_100_1.pdf}%
}}\\[0.5cm]% If you want some vertical space
\makebox[\textwidth]{%
\subfigure[MR1]{%
\includegraphics[width=0.49\textwidth]{./Pics1/mr1_fixed/mr1_fixed_middle_1.pdf}%
}%
\hfill    
\subfigure[MR10]{%
\includegraphics[width=0.49\textwidth]{./Pics1/mr10_fixed/mr10_fixed_middle_1.pdf}%
}}\\[0.5cm]% If you want some vertical space
\makebox[\textwidth]{%
\subfigure[MR1]{%
\includegraphics[width=0.49\textwidth]{./Pics1/mr1_fixed/mr1_fixed_end_2.pdf}%
}%
\hfill    
\subfigure[MR10]{%
\includegraphics[width=0.49\textwidth]{./Pics1/mr10_fixed/mr10_fixed_end_2.pdf}%
}}%
\caption{Comparing MR1 and MR10 cases using fixed mesh. Simulation time step increases from top to bottom and from (a) t=100(start) to (c) t=3000(end).}
\label{fig:1testcase}
\end{figure}

@@

\medskip
At this point we have to mentioned one more set of simulations, based on the work of \citet{saffman_1986}. The Hele-shaw cell, a geometrical domain as this is defined by experimental studies and is presented in figures \ref{fig:1a_homoheleshaw_3}, \ref{fig:1b_homoheleshaw_3} and fig. \ref{fig:1c_homoheleshaw_3} is used. In all cases, simulations were performed in a squared geometry of $5x5$, where fluid $1$ is added into the domain at the bottom left-hand side corner with a velocity (magnitude) of 0.7071 %(i.e., sqrt(2*0.25))
. The sink (pressure is set to $0$) is allocated in the top right hand side corner of the domain. Newmann boundary conditions %(i.e., no flux) 
was imposed to all borders of the domain except at the top righ hand side corner. The mobility ratios for these $3$ cases are $3$ and $10$ while for the latter, homogeneous and heterogeneous domain is used.

>>>>

\medskip
In this section three different sets of simulations were explained. Starting from an initial square set-up to validate the existance of cross flow and how the simulator works, we moved to a larger domain by increasing the aspect ratio. The reason was to give more time, space and greater number of elements to our simulator and again see how the front/cross-flow will develop. The third test-case is based in the initial and boundary condition of the second set of simulations. Now we would like to know what is the impact of different mobility ratios (see Fig.\ref{fig:1testcase}) and how the cross-flow as well as the simulation will progress on time. The purpose of these three cases was to verify that our model is working for cross flow cases thus will allow to proceed further and expand this technique into more complex formations.

\begin{figure}[h]
\makebox[\textwidth]{%
\subfigure[MR1]{%
\includegraphics[width=0.49\textwidth]{./Pics1/mr1_fixed/mr1_fixed_100_2.pdf}%
}%
\hfill    
\subfigure[MR10]{%
\includegraphics[width=0.49\textwidth]{./Pics1/mr10_fixed/mr10_fixed_100_1.pdf}%
}}\\[0.5cm]% If you want some vertical space
\makebox[\textwidth]{%
\subfigure[MR1]{%
\includegraphics[width=0.49\textwidth]{./Pics1/mr1_fixed/mr1_fixed_middle_1.pdf}%
}%
\hfill    
\subfigure[MR10]{%
\includegraphics[width=0.49\textwidth]{./Pics1/mr10_fixed/mr10_fixed_middle_1.pdf}%
}}\\[0.5cm]% If you want some vertical space
\makebox[\textwidth]{%
\subfigure[MR1]{%
\includegraphics[width=0.49\textwidth]{./Pics1/mr1_fixed/mr1_fixed_end_2.pdf}%
}%
\hfill    
\subfigure[MR10]{%
\includegraphics[width=0.49\textwidth]{./Pics1/mr10_fixed/mr10_fixed_end_2.pdf}%
}}%
\caption{Comparing MR1 and MR10 cases using fixed mesh using the same map of permeabilities as test-case in Fig.\ref{fig:testcase}. Simulation time step increases from top to bottom and from (a,b) t=100(start) to (e,f) t=3000(end).}
\label{fig:1testcase}
\end{figure}

@@

\medskip
Based on the work of \citet{saffman_1986}, the Hele-shaw cell, a geometrical domain as this is defined by experimental studies and is presented in Figures \ref{fig:1a_homoheleshaw_3}, \ref{fig:1b_homoheleshaw_3} and fig. \ref{fig:1c_homoheleshaw_3} will be used for the next set of simulations. In all cases, simulations were performed in a squared geometry of $5\times5$, where fluid $1$ is added into the domain at the bottom left-hand side corner with a velocity (magnitude) of 0.7071 %(i.e., sqrt(2*0.25))
. The sink (pressure is set to $0$) is allocated in the top right hand side corner of the domain. Newmann boundary conditions %(i.e., no flux) 
was imposed to all borders of the domain except at the top righ hand side corner. The mobility ratios for these $3$ cases are $3$ and $10$ while for the latter, homogeneous and heterogeneous domain is used.
